Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2024-08-22 Thesis/04-chap4.qmd
small revisions for the first sections of chapter 4

In @sec-autovi-implementation, we discussed how `autovi` relies on several Python libraries, with a particularly strong dependency on `TensorFlow`. Managing a Python environment and correctly installing `TensorFlow` on a local machine can be challenging for many users. Moreover, `TensorFlow` is a massive library that undergoes continuous development, which inevitably leads to compatibility issues arising from differences in library versions. These challenges can create significant barriers for users who want to perform residual assessments with the `autovi` package.

@@

`autovi.web` is available at [autoviweb.netlify.app](autoviweb.netlify.app). The implementation discussed in this chapter is based on `autovi.web` version 0.1.0. By providing this web interface, we aim to significantly reduce the technical hurdles associated with using `autovi`, making advanced residual assessment techniques more accessible to a wider audience of researchers and data analysts. This approach aligns with modern trends in data science tools, where web-based interfaces are increasingly used to make advanced analytical techniques more widely available.

@@

`autovi.web` is a web application built using the `shiny` [@shiny] and `shinydashboard` [@shinydashboard] R packages. Hosted on the [shinyapps.io](https://www.shinyapps.io) domain, the application is accessible through any modern web browser.Additionally, R packages `htmltools` [@htmltools] and `shinycssloaders` [@shinycssloaders] are used to render markdown document in shiny application, and add loading animation for shiny widgets, respectively.

In our initial planning for `autovi.web`, we considered implementing the entire web application using the `webr` framework [@webr], which would have allowed the entire application to run directly in the user's browser. However, this approach was not feasible at the time of writing this chapter. The reason is that one of the R packages `autovi` depends on the R package `splancs` [@splancs], which uses compiled Fortran code. Unfortunately, a working Emscripten version of this package, which would be required for `webr`, was not available.

@@

### Workflow

The workflow of `autovi.web` is designed to be straightforward, with numbered steps displayed in the main user interface as shown in @fig-autovi-web. Since the design details have already been covered in @sec-autovi-web-design, we will not repeat the functionality of each panel in this section.

For general users, the workflow starts with Step 1: uploading a CSV file by clicking the "upload CSV" button. A window will pop up, allowing the user to select the CSV file. The CSV file should contain at least two columns representing fitted values and residuals of a residual plot. If a lineup needs to be evaluated, the CSV file should contain an additional column for labels of residual plot.  In Step 2, the user specifies the CSV type based on the uploaded file, choosing between a single residual plot or a lineup of multiple residual plots. Step 3 involves selecting the appropriate columns for fitted values, residuals, and, optionally, labels of residual plots, from the dataset. In Step 4, the user sets the number of bootstrapped draws needed for the analysis; more draws provide a better estimate of the bootstrapped distribution but result in slower computation. The user should also set the seed to control the simulation. If the dataset contains a lineup and the true residual plot is known, select its label. Finally, clicking the play button will initiate the analysis, and the user can review the result panels.

@@

>>>>

The web interface, called `autovi.web`, builds on `autovi` to provide potential users easier access to automated residual plot assessment. It eliminates software installation issues, so users no longer need to struggle with managing Python environments or installing and maintaining the correct versions of libraries. The interface is cross-platform available across devices and operating systems, and accessible to users without R programming knowledge. An added benefit is that updates can be controlled centrally so that users will always have the latest features.

<!-- In @sec-autovi-implementation, we discussed how `autovi` relies on several Python libraries, with a particularly strong dependency on `TensorFlow`. Managing a Python environment and correctly installing `TensorFlow` on a local machine can be challenging for many users. Moreover, `TensorFlow` is a massive library that undergoes continuous development, which inevitably leads to compatibility issues arising from differences in library versions. These challenges can create significant barriers for users who want to perform residual assessments with the `autovi` package.

@@

`autovi.web` is available at [autoviweb.netlify.app](autoviweb.netlify.app). The implementation discussed in this chapter is based on `autovi.web` version 0.1.0. By providing this web interface, we aim to significantly reduce the technical hurdles associated with using `autovi`, making advanced residual assessment techniques more accessible to a wider audience of researchers and data analysts. This approach aligns with modern trends in data science tools, where web-based interfaces are increasingly used to make advanced analytical techniques more widely available.
-->

@@

`autovi.web` is built using the `shiny` [@shiny] and `shinydashboard` [@shinydashboard] R packages. Hosted on the [shinyapps.io](https://www.shinyapps.io) domain, the application is accessible through any modern web browser. The R packages `htmltools` [@htmltools] and `shinycssloaders` [@shinycssloaders] are used to render markdown documentation in shiny application, and for loading animations for shiny widgets, respectively.

Determining the best way to implement the interface was difficult. In our initial planning for `autovi.web`, we considered implementing the entire web application using the `webr` framework [@webr], which would have allowed the entire application to run directly in the user's browser. However, this approach was not feasible at the time of writing this chapter. The reason is that one of the R packages `autovi` depends on the R package `splancs` [@splancs], which uses compiled Fortran code. A working Emscripten (XXX reference?) version of this package, which would be required for `webr`, was not available.

@@

### Usage, from the user perspective

The user would follow the order of the numbered steps displayed in the main user interface as shown in @fig-autovi-web, <!--Since the design details have already been covered in @sec-autovi-web-design, we will not repeat the functionality of each panel in this section.-->
as follows:

- Step 1: uploading a CSV file by clicking the "upload CSV" button. A window will pop up, allowing the user to select the CSV file. The CSV file should contain at least two columns representing fitted values and residuals of a residual plot. If a lineup needs to be evaluated, the CSV file should contain an additional column for labels of residual plot.  
- In Step 2, the user specifies the CSV type based on the uploaded file, choosing between a single residual plot or a lineup of multiple residual plots. 
- Step 3 involves selecting the appropriate columns for fitted values, residuals, and, optionally, labels of residual plots, from the dataset. 
- In Step 4, the user sets the number of bootstrapped draws needed for the analysis; more draws provide a better estimate of the bootstrapped distribution but result in slower computation. The user should also set the seed to control the simulation. If the dataset contains a lineup and the true residual plot is known, select its label. 
- Finally, clicking the play button will initiate the analysis, and the user can review the result panels.

@@

## Availability

The web interface is housed at [autoviweb.netlify.app](autoviweb.netlify.app).

The source code for both packages are available at XXX, and the current version of `autovi` can be installed from CRAN.
